---
title: "contamination by phenotype"
author: "Victor Yuan"
date: "31/08/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Set up

```{r, message = FALSE, warning = FALSE}
library(pheatmap)
library(tidyverse)
library(viridis)
library(ggrepel)
library(planet)
library(broom)
library(scales)

ss <- read_csv(here::here('data', 'raw', '1-3_ss.csv'))

# color key
color_code <- readRDS('Z:/Victor/Projects/NIH - cells/data/main/interim/2_3_color_code.rds')
color_code_tissue <- setNames(color_code$Colors_Tissue, gsub(' cs', '',color_code$label))

color_code_tissue <- c(color_code_tissue, 'nRBC' = 'grey')
color_code_tissue <- c(color_code_tissue, 'Syncytiotrophoblast' = '#f4702e')
colors <- readRDS(here::here('data', 'r objects', 'dataset-colors.rds'))
```

# linear modelling

```{r}
ss %>%
  filter(Tissue == 'Villi') %>%
  ggplot(aes(x = Group, y = prob_snp_outlier )) +
  geom_boxplot() +
  facet_grid(cols = vars(dataset), 
             scale = 'free_x')
```

Missing group variables for some datasets

Grab em from original ss

dataset 8 has many variables to potentially test, neurobehaviour, omit
dataset 9 has arsenic, doesn't make sense to test, omit

dataset 5,7 and 10 have other tissues / no villi / no phenotype

dataset 11 does not have any metadata to test against

```{r}
ss_GSE125605 <- read_csv('Z:/7_ExternalData/GSE125605/GSE125605_ss.csv')
ss <- ss %>% 
  left_join(ss_GSE125605 %>%
              mutate(Group = Pathology) %>%
              select(Sample_Name, Group), by = 'Sample_Name') %>%
  mutate(Group = coalesce(Group.x, Group.y)) %>%
  select(-Group.x, -Group.y)

ss_GSE75196 <- read_csv('Z:/7_ExternalData/GSE75196/GSE75196_ss.csv')
ss <- ss %>% 
  left_join(ss_GSE75196 %>%
              mutate(Group = Pathology) %>%
              select(Sample_Name, Group),
            by = 'Sample_Name') %>%
  mutate(Group = coalesce(Group.x, Group.y)) %>%
  select(-Group.x, -Group.y)


ss %>%
  filter(Tissue == 'Villi', !is.na(Group)) %>%
  ggplot(aes(x = Group, y = prob_snp_outlier )) +
  geom_boxplot() +
  facet_grid(cols = vars(dataset), 
             scale = 'free_x') + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(angle = 0, vjust = 0.5),
    axis.line = element_line(),
    #axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.spacing.x = unit(0, "lines"),
    strip.background = element_rect(color = NA, fill = NA))+
  labs(x ='', y = 'P(outlier)')
```

## Stats

```{r}
ss %>%
  filter(Tissue == 'Villi', !is.na(Group)) %>%
  nest(data = -c(dataset)) %>%
  mutate(lm = map(data, ~lm(prob_snp_outlier ~ Group, .) %>%
                    tidy())) %>%
  unnest(lm) %>%
  select(-data) %>%
  filter(term != '(Intercept)')
```

None statistically significantly increased

```{r}
ss %>%
  filter(Tissue == 'Villi', !is.na(Group)) %>%
  nest(data = -c(dataset)) %>%
  mutate(lm = map(data, ~lm(PC1_mbd500 ~ Group, .) %>%
                    tidy())) %>%
  unnest(lm) %>%
  select(-data) %>%
  filter(term != '(Intercept)')
```


```{r}
```
