---
title: "Validating with microsatellites"
author: "Victor Yuan"
output: html_document
editor_options: 
  chunk_output_type: inline
---

To test if there is correlation between DNAm-based contamination and microsatellites

## Load methylation data

```{r, message = FALSE}
library(tidyverse)
library(planet)
library(readxl)
library(broom)
library(ggrepel)

ss <- read_csv(here::here('data', 'raw', '1-4_ss.csv'))

# color key
color_code <- readRDS('Z:/Victor/Projects/NIH - cells/data/main/interim/2_3_color_code.rds')
color_code_tissue <- setNames(color_code$Colors_Tissue, gsub(' cs', '',color_code$label))

color_code_tissue <- c(color_code_tissue, 'nRBC' = 'grey')
color_code_tissue <- c(color_code_tissue, 'Syncytiotrophoblast' = '#f4702e')
colors <- readRDS(here::here('data', 'r objects', 'dataset-colors.rds'))
# ggplot
colors_tissue <- c('Amnion' = '#26A9AD', 
                   'Basal plate' = '#FEDBF4',
                   'Chorion' = '#FF3300',
                   'Cytotrophoblast' = '#FBC02D',
                   'Decidua' = '#FF2BFF',
                   'Maternal Blood' = '#6396F2',
                   'Villi' = '#BDB9B7',
                   'Villi maternal' = 'lightblue')

```
### Maternal villi and amnion/chorion

Ok, lastly: PM372, PM375, PM376 are  maternal villi samples

These I had not originally analyzed in this project. I processed these samples and last thing to do is apply the pca projection.

```{r}
# load the methylation data and apply pca
ss_vm <- read_csv(here::here('data', 'r objects', '0-1_ss-vm.csv'))
bmiq_vm <- readRDS(here::here('data', 'r objects', '0-1_bmiq-vm.rds'))

#script to project pca
source(here::here('r', 'project_mbd_pca.R'))

pca_mbd <- project_mbd_pca(bmiq_vm)
pca_mbd
```


```{r}
ss <- bind_rows(ss %>% mutate(dataset = as.character(dataset)),
          ss_vm %>% 
  select(Sample_Name, Sex, prob_snp_outlier, contains('normalized_'), 
         controls_failed:GA_epi_RRPC) %>%
  mutate(dataset = 'villi maternal',
         dataset_label = 'Villi (maternal side)',
         Group = 'Healthy', dataset_label_short = 'vm',
         Tissue_gen = 'Placenta', Tissue_gen2 = 'Placenta (Villi maternal)'))

ss <- ss %>%
  left_join(pca_mbd, by= 'Sample_Name')

ss %>% 
  mutate(dataset = as.character(dataset)) %>%
  ggplot(aes(x = PC1_mbd500.y, y = dataset, fill = Tissue)) +
  geom_boxplot() +
  theme_bw()  +
  theme(panel.border = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.ticks = element_blank(),
        axis.line =element_line()) #+
  scale_fill_manual(values = colors_tissue)
```
## Load microsatellite data

```{r}
data_micro1 <- readxl::read_xlsx(
  here::here('data', 'microsatellites', 
             'Contamination study result database_EA.xlsx'))

data_micro2 <- readxl::read_xlsx(
  here::here('data', 'microsatellites', 
             '2022-03-03 Aminion Contamination Data.xlsx')) 

data_micro <- 
  bind_rows(data_micro1, 
          data_micro2 %>% 
            mutate(`ALELLE 1 size` = as.character(`ALELLE 1 size`),
                   `ALELLE 2 size` = as.character(`ALELLE 2 size`),
                   `ALELLE 3 size` = as.character(`ALELLE 3 size`),
                   `ALELLE 4 size` = as.character(`ALELLE 4 size`),
                   `ALELLE 2 area` = as.character(`ALELLE 2 area`),
                   `ALELLE 3 area` = as.character(`ALELLE 3 area`)))
```

The column `SAMPLE ID` will serve as base to create the following new columns:

- Sample_Name: should match the sample names in DNAm ss
- Tissue
- Case ID: Right now case ID is incomplete

# Data cleaning Sample_Name

```{r}
sum(data_micro$`SAMPLE ID` %in% ss$Sample_Name)
```
No matches currently

```{r}
# create a working copy of the data
d <- data_micro

d %>% select(`SAMPLE ID`)
```
### Add underscore:

```{r}
d <- d %>% 
  mutate(Sample_Name = 
           
           # add underscore between case and tissue
           sub('(\\d) *(\\D)', '\\1_\\2', `SAMPLE ID`))
d %>% 
  select(Sample_Name, `SAMPLE ID`)  
```
### Remove space and following 

```{r}
d <- d %>% 
  mutate(Sample_Name = 
           
           #remove everything after the space
           sub(' .*',  '', Sample_Name))

d %>% select(Sample_Name, `SAMPLE ID`) %>%
  filter(grepl(' .*', `SAMPLE ID`)) %>% head 
```
### Remove asterisk

```{r}
d <- d %>%
  mutate(Sample_Name = sub('\\*',  '', Sample_Name))

d %>% select(Sample_Name, `SAMPLE ID`) %>%
  filter(grepl('\\*', `SAMPLE ID`)) 
```
### Check matches

```{r}
sum(d$Sample_Name %in% ss$Sample_Name)
```
### "_v" not "_vc"

Some FTs need to be "_v" instead of "_vc"

```{r}
d %>%
  select(Sample_Name) %>%
  filter(grepl('(FT)(38|39|41|42|59|60)_vc', Sample_Name)) %>% distinct()
```

```{r}
ss  %>%
  select(Sample_Name) %>%
  filter(grepl('(FT)(38|39|41|42|59|60)_v+', Sample_Name))
```
```{r}
d <- d %>% 
  mutate(Sample_Name = gsub('(FT)(38|39|41|42|59|60)_vc', '\\1\\2_v',
                            Sample_Name))
d %>% 
  select(Sample_Name, `SAMPLE ID`) %>%
  filter(grepl('(FT)(38|39|41|42|59|60)_v.*', Sample_Name))
```

```{r}
sum(d$Sample_Name %in% ss$Sample_Name)
```
### NTD_3_v not NTD3_vc

There's a space between the letters and numbers in `ss`, but not `d`. They also are denoted as "vc" in `d`, but "v" in `ss`.

```{r}
d %>%
  select(Sample_Name, `SAMPLE ID`) %>%
  filter(grepl('NTD(3|9)_vc', Sample_Name)) %>% distinct()
```

```{r}
ss %>%
  select(Sample_Name) %>%
  filter(grepl('NTD_(3|9)_v.*', Sample_Name))
```

```{r}
d <- d %>%
  mutate(Sample_Name = gsub('(NTD)(3|9)_vc', '\\1_\\2_v',  
                                Sample_Name))

d %>%
  select(Sample_Name, `SAMPLE ID`) %>%
  filter(grepl('NTD(3|9)v.*', `SAMPLE ID`)) %>% distinct()
```

```{r}
sum(d$Sample_Name %in% ss$Sample_Name)
```

### PL64 PL96

Why are  PL64, PL96 not matching: 
```{r}
ss %>% filter(grepl('PL64|PL96', Sample_Name)) %>%
  arrange(Sample_Name) %>% 
  pull(Sample_Name) 
```

```{r}
d %>% 
  filter(grepl('(PL64|PL96)_(r|v).*', Sample_Name)) %>% 
  select(Sample_Name, `SAMPLE ID`)
```
PL64_r2vc -> PL64_r2
PL96_v1v2vc -> PL96v1v2

```{r}
d <-d %>%
  mutate(Sample_Name = gsub('PL64_r2vc', 'PL64_r2',  
                                gsub('PL96_v1v2vc', 'PL96v1v2', 
                                     Sample_Name))) 

d %>% 
  filter(grepl('PL64_r2|PL96v1v2', Sample_Name)) %>% 
  select(Sample_Name, `SAMPLE ID`)
```
```{r}
sum(d$Sample_Name %in% ss$Sample_Name)
```
### villi maternal

```{r}
d <-d %>%
  mutate(Sample_Name = gsub('_vm', '_mv',  Sample_Name))

d %>% 
  filter(grepl('mv', Sample_Name)) %>% 
  select(Sample_Name, `SAMPLE ID`)
```

# Case_id

```{r}
d %>%
  pull(Sample_Name)
```
```{r}
d <- d %>%
  mutate(case_id = str_extract(Sample_Name, '[:alnum:]+'))

d %>%
  select(Sample_Name, case_id) %>% distinct() %>% arrange(case_id)
```
NTD_3, NTD_9 need fixing since they have an underscore in the middle

```{r}
d <- d %>%
  mutate(case_id = ifelse(case_id == 'NTD',
                          str_replace(Sample_Name, '(NTD)_(3|9).*', '\\1\\2'),
                          case_id))

d  %>%
  select(Sample_Name, `SAMPLE ID`, case_id) %>%
  filter(grepl('NTD_(3|9).*', Sample_Name))

d$case_id
```
PL96v1v2 needs fixing

```{r}
d <- d %>%
  mutate(case_id = ifelse(case_id == 'PL96v1v2', 'PL96', case_id))
```

## Tissue

```{r}
d$Sample_Name %>%
  str_replace('[:alpha:]+[:digit:]+_*', '') %>% unique()
```

```{r}
d <- d %>% 
  mutate(Tissue = case_when(
    grepl('v[^m]', Sample_Name) ~ 'Villi',
    grepl('v$', Sample_Name) ~ 'Villi',
    grepl('mv', Sample_Name) ~ 'Villi maternal',
    grepl('r2', Sample_Name) ~ 'Villi',
    grepl('dec', Sample_Name) ~ 'Decidua',
    grepl('matwb', Sample_Name) ~ 'Maternal blood',
    grepl('am', Sample_Name) ~ 'Amnion',
    grepl('ch', Sample_Name) ~ 'Chorion'
  )) 
d %>%
  select(Sample_Name, Tissue)
```


## Join microsatellite data `d` to dnam data `ss`

Compare the list I sent to EA/MP originally to make sure all samples accounted for:

```{r}
samples <- 
  read_csv(here::here('data', 'raw', '1-6_DNAm contamination Victor follow-up samples.csv'))

all(samples$Sample_Name %in% ss$Sample_Name)
```

```{r}
all(samples$Sample_Name %in% d$Sample_Name)
```
After accounting for all matches, we can join:

```{r}
data <- d %>% 
  rename(Sample_Name_microsat = `SAMPLE ID`) %>%
  select(Sample_Name, case_id, Tissue, `Approx % contamination`, 
         `MARKER TESTED`,`PCR date (yyyy-mm-dd)`,                                       
         `Analyzer Date (mm-dd-yy)` , result, coments ) %>%
  mutate(`Approx % contamination` = as.numeric(`Approx % contamination`)) %>%
  
  left_join(ss %>% select(-Tissue), 
            by= 'Sample_Name')

data
```

# Compare micro vs dna-contam

```{r}
data %>% 
  filter(!is.na(`Approx % contamination`) &
           !is.na(prob_snp_outlier))  %>%
  pull(Sample_Name) %>% unique %>% length
  
```
There are 22 villi samples that have microsat data. 3 additional for the maternal villi.

Evie recently sent additional chorion samples, that will be included later.

### P(SNPoutlier)

```{r}
data %>% 
  filter(!is.na(`Approx % contamination`) &
           !is.na(prob_snp_outlier)) %>%
  {
    ggplot(data =., aes(x = prob_snp_outlier, y = `Approx % contamination`)) +
      geom_point() +
      geom_smooth(method = 'lm') +
      geom_text_repel(data = . %>%
                        filter(
                          grepl('(_)(mv|ch|am)', Sample_Name)
                          #prob_snp_outlier > 0.125
                          ),
                      aes(label = Sample_Name),
                      nudge_y = 5) +
      labs(x = "P(outlier)", y = '% contamination (microsatellites)') +
      theme_bw() +
      theme(panel.border = element_blank(), 
        panel.grid.minor.y = element_blank(),
        axis.ticks = element_blank(),
        axis.line =element_line())
  }
```

is it significant?

```{r}
lm( `Approx % contamination` ~ prob_snp_outlier,
  data = data %>%
  filter(!is.na(`Approx % contamination`) &
           !is.na(prob_snp_outlier))) %>%
  tidy()
```
p = 0.0335

What are those outliers?
```{r}
data %>% 
  filter(!is.na(`Approx % contamination`) &
           !is.na(prob_snp_outlier),
         `Approx % contamination` > 4) 
```
Is it still significant after removing those high samples?

```{r}
data %>% 
  filter(!is.na(`Approx % contamination`) &
           !is.na(prob_snp_outlier),
         
         `Approx % contamination` < 8) %>%
  ggplot(aes(x = prob_snp_outlier, y = `Approx % contamination`)) +
  geom_point() +
  geom_smooth(method = 'lm') 
```

### PC1 

```{r}
data %>%
  filter(!is.na(`Approx % contamination`) &
           !is.na(prob_snp_outlier),
         !is.na(PC1_mbd500_category)) %>%
  mutate(PC1_mbd500_category = fct_reorder(PC1_mbd500_category, PC1_mbd500)) %>%
  ggplot(aes(x = PC1_mbd500_category, y= `Approx % contamination` )) +
  geom_boxplot() +
  geom_jitter()
```
```{r}
data %>%
  filter(!is.na(`Approx % contamination`) &
           !is.na(prob_snp_outlier)) %>%
  ggplot(aes(x = PC1_mbd500, y= `Approx % contamination` )) +
  geom_point() +
  geom_smooth(method = 'lm')

# exclude villi maternal


```
seems like a relationship exists, is it statistically significant?

```{r}
lm( `Approx % contamination` ~ PC1_mbd500,
  data = data %>%
  filter(!is.na(`Approx % contamination`) &
           !is.na(prob_snp_outlier))) %>%
  glance()
```
p = 3.2e-17

Remove pl31 am ch

```{r}
data %>% 
  filter(!is.na(`Approx % contamination`) &
           !is.na(prob_snp_outlier),
         
         `Approx % contamination` < 8) %>%
  ggplot(aes(x = PC1_mbd500, y= `Approx % contamination` )) +
  geom_point() +
  geom_smooth(method = 'lm')
```





